### 2017-11-21 manuscript.rmd
silenced simmap output for palpons and sex, placed upstream

```{r simmap_making, echo=F, message=F, warning=F}
#Stochastic trait mapping:
#Make simmap objects
#print("SIMMAP Sex Distribution")
make.simmap(ultratree, sex, nsim = 100, message=FALSE) -> sex_sim
#print("SIMMAP Palpons")
make.simmap(ultratree, palpons, nsim = 100, message=FALSE) -> palpons_sim
#print("SIMMAP Tentilla")
make.simmap(ultratree, tentilla, nsim = 100, message=FALSE) -> tentilla_sim
#print("SIMMAP Tentilla2")
make.simmap(ultratree, tentilla2, nsim = 100, message=FALSE) -> tentilla_sim2
#print("SIMMAP Nectosome")
make.simmap(ultratree, nectosome, nsim = 100, message=FALSE) -> nectosome_sim
#print("SIMMAP Nectosome Position")
make.simmap(ultratree, necto_pos, nsim = 100, message=FALSE) -> necto_pos_sim
#print("SIMMAP Nectophore Types")
make.simmap(ultratree, necto_types, nsim = 100, message=FALSE) -> necto_types_sim
#print("SIMMAP Bracts")
make.simmap(ultratree, bracts, nsim = 100) -> bracts_sim
#print("SIMMAP Habitat")
make.simmap(ultratree, vrange, nsim = 100, message=FALSE) -> vrange_sim

@@

When we reconstruct the evolutionary history of different traits in siphonophore species, we obtain the following results:

#####SIMMAP Sex distribution
```{r sex, echo=F, message=F, warning=F}
#Simmap SEX
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Dioecious", "Monoecious")
sex_sim %>% plotSimmap(lwd = 4, add = T, colors=colors)
nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(sex_sim)
```

Posterior probabilities of states (0 Dioecious, 1 Monoecious).

#####SIMMAP Presence of palpons
```{r palpons, echo=F, message=F, warning=F}
#Simmap PALPONS
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
palpons_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(palpons_sim)
```

@@

*Physalia physalis* may have reduced tentilla, which would indicate there was only one loss of tentilla at the branch leading to *Apolemia*.

@@

#####Phylogenetic signal in VARS bathymetrics
```{r phylosig_depth, echo=F, message=F, warning=F}
depth_physig
depth_multisig
```

>>>>

```{r simmap_making, echo=F, message=F, warning=F, include=F}
#Stochastic trait mapping:
#Make simmap objects
#print("SIMMAP Sex Distribution")
make.simmap(ultratree, sex, nsim = 100, message=FALSE) -> sex_sim
#print("SIMMAP Palpons")
make.simmap(ultratree, palpons, nsim = 100, message=FALSE) -> palpons_sim
#print("SIMMAP Tentilla")
make.simmap(ultratree, tentilla, nsim = 100, message=FALSE) -> tentilla_sim
#print("SIMMAP Tentilla2")
make.simmap(ultratree, tentilla2, nsim = 100, message=FALSE) -> tentilla_sim2
#print("SIMMAP Nectosome")
make.simmap(ultratree, nectosome, nsim = 100, message=FALSE) -> nectosome_sim
#print("SIMMAP Nectosome Position")
make.simmap(ultratree, necto_pos, nsim = 100, message=FALSE) -> necto_pos_sim
#print("SIMMAP Nectophore Types")
make.simmap(ultratree, necto_types, nsim = 100, message=FALSE) -> necto_types_sim
#print("SIMMAP Bracts")
make.simmap(ultratree, bracts, nsim = 100) -> bracts_sim
#print("SIMMAP Habitat")
make.simmap(ultratree, vrange, nsim = 100, message=FALSE) -> vrange_sim

@@

#####SIMMAP Sex distribution
```{r sex, echo=F, message=F, warning=F, include=F}
#Simmap SEX
#plotTree(ultratree, lwd = 4)
#colors = c("black", "red")
#names(colors) = c("Dioecious", "Monoecious")
#sex_sim %>% plotSimmap(lwd = 4, add = T, colors=colors)
#nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
#add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(sex_sim)
```

#####SIMMAP Presence of palpons
```{r palpons, echo=F, message=F, warning=F, include=F}
#Simmap PALPONS
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# palpons_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(palpons_sim)
```

@@

@@
